---
title: "Lab 1 Answers: Intro to R"
author: "Dr. Ryan Johnson"
date: "`r Sys.Date()`"
output: openintro::lab_report
---

```{r load-packages, message=FALSE}
library(tidyverse)
library(openintro)
data("arbuthnot")
```

## Exercise 1

What command would you use to extract just the counts of girls baptized?  In these lab reports, also use complete sentences and the text -> code -> text -> code pattern described in the video above.

### Answer:
We would use this command:

```{r view-girls-counts}
arbuthnot$girls
```

### Grading
3 points for the correct code.  1 point for at least one sentence that uses correct grammar and punctuation.  (4 points total)

## Exercise 2
Is there an apparent trend in the number of girls baptized over the years? How would you describe it? (To ensure that your lab report is comprehensive, be sure to include the code needed to make the plot as well as your written interpretation.)

#### Answer:
The text of answers may vary.    
```{r trend-girls}
ggplot(arbuthnot, aes(x = year, y = girls)) +
  geom_line()
```

### Grading
2 points for saying something correct (take off 0.5 - 1 point if answer is super vague).  Be wary of well polished answers because answers to these labs may exist online.  You can use TurnItIn2's utility to check if their answer matches someone else's online.

1 point for communication (complete sentences, spelling, grammar)

3 points for the plot (dot plot is also fine)

## Exercise 3

Now, generate a plot of the proportion of boys born over time. What do you see?

### Answer
Text of answers may vary.

```{r plot-prop-boys-arbuthnot}
arbuthnot <- arbuthnot %>%
  mutate(total = boys + girls)
arbuthnot <- arbuthnot %>%
  mutate(boy_proportion = boys / total)
ggplot(arbuthnot, aes(x = year, y = boy_proportion)) +
  geom_point()
```

### Grading
2 points for saying something correct (take off 0.5 - 1 point if answer is vague).  1 point for noticing that all proportions are above 50%.

1 point for communication (complete sentences, spelling, grammar)

3 points for the plot (line plot is also fine)

## Exercise 4

What years are included in this data set? What are the dimensions of the data frame? What are the variable (column) names?


### Answer
The years included in this data set are 1940-2002.  The dataset has 63 rows and 3 columns.  The column names are `year`, `boys`, and `girls`.

(They might include the code below, but it it not necessary)
```{r dim-present}
data(present)
glimpse(present)
```
### Grading
1 point for 1940, 1 point for 2002, 1 point for 63 rows.  1 point for 3 columns.  1 point each for `year`, `boys`, and `girls`, respectively.  1 point for communication.

## Exercise 5

How do these counts compare to Arbuthnot’s? Are they of a similar magnitude?


### Answer
Answers may vary.  Their answer should include the fact that the counts from the `present` data are more than 300 times larger than `arbuthnot`'s. 

```{r count-compare}
mean(present$boys) / mean(arbuthnot$boys)
```
### Grading
3 points for noting the size difference.  1 point for quantifiying the size difference in some way, such as "over 300." 1 point for communicaiton.

## Exercise 6

Make a plot that displays the proportion of boys born over time. What do you see? Does Arbuthnot’s observation about boys being born in greater proportion than girls hold up in the U.S.? Include the plot in your response. Hint: You should be able to reuse your code from Exercise 3 above, just replace the name of the data frame.

### Answer

The code for their plots might differ from mine, but the plot should be the same.  Unless they made a dot plot instead of a line plot, which is also fine.

It appears that Arbuthnot’s observation about boys being born in greater proportion than girls holds up in the U.S.
```{r plot-prop-boys-present}
present %>%
  mutate(boy_prop = boys/(boys+girls)) %>%
  ggplot(aes(x = year, y = boy_prop)) +
  geom_line()
```
### Grading

3 points for the plot, 2 points for observing that boys are born in higher proportion than girls in the US, 1 point for communication.

## Exercise 7

Create a new variable for the present data called total that adds up boys and girls just like we did with arbuthnot’s. For this question, you only need to present the code you used as an code chunk.

### Answer
```{r find-max-total}
present <- present %>%
  mutate(total = boys + girls)
```

### Grading
3 points for code similar to mine that works.

## Exercise 8

In what year did we see the most total number of births in the U.S.? Hint: Sort your dataset in descending order based on the total column. You can do this interactively in the data viewer by clicking on the arrows next to the variable names. To include the sorted result in your report you will need to use two new functions. First we use arrange() to sorting the variable. Then we can arrange the data in a descending order with another function, desc(), for descending order. The sample code is provided below.

### Answer

The code below shows 1961 was the year with the highest number of total births.

```{r 8a}
present %>%
  arrange(desc(total))
```
### Grading

3 points for 1961. 1 point for including code.  1 point for communication.

## Exercise 9

Use complete sentence(s) to tell me when you need to install packages and when you need to load packages with the library function.

### Answer

You only need to install packages once on a computer.  You need to load packages you need each time you start R.

### Grading

1 point for installing once.  1 point for loading each time.  1 point for communication.

## Exercise 10
Use complete sentence(s) to tell me the three ways to view data.

### Answer
One way to view data is to use the code `View(your-data-frame)`.  A second way to view data is to click on the name of the data set in the "Envirorment" pane.  A third way to view data is simply to put it's name in the console such as `your-data-frame.`

### Grading
1 point for each way.  1 point for communication.
