---
title: "Lab 2 Answers"
author: "Dr. Johnson"
date: "`r Sys.Date()`"
output: openintro::lab_report
---

```{r load-packages, message=FALSE}
library(tidyverse)
library(openintro)
data(nycflights)
```


## Exercise 1

Using what we learned from section 1.2 from the textbook, what kind of variable is the variable `dep_delay`?  What kind of variable is `carrier`? (Remember to use complete sentences in your lab reports)

### Answer:

The variable `dep_delay` is a numerical continuous variable.  The variable `carrier` is a categorical variable.



### Grading

2 points for each variable.  2 points for using complete sentences with correct grammar.  Partial credit for partially correct answers.

## Exercise 2
Put each of the three histograms into your lab report. How do they compare? Are features revealed in one that are obscured in another?

### Answer:

```{r 2-a}
ggplot(data = nycflights, aes(x = dep_delay)) +
  geom_histogram()
```

```{r 2-b}
ggplot(data = nycflights, aes(x = dep_delay)) +
  geom_histogram(binwidth = 15)
```

```{r 2-c}
ggplot(data = nycflights, aes(x = dep_delay)) +
  geom_histogram(binwidth = 150)
```

Answers to the questions may vary.  They might talk about how the histogram with the narrowest bins shows that the vast majority of flights are not delayed, and some flights even leave early.

### Grading

2 points per histogram.  Regarding the second part of the question, 2 points for saying something correct, 1 point for sentence/grammar.

## Exercise 3
Copy the code from the code block above into a code block in your lab report.  Write another line that will tell you how many flights are in this data frame.  (Hint: it's a command that is present somewhere above)

### Answer
```{r}
sfo_feb_flights <- nycflights %>%
  filter(dest == "SFO", month == 2)
glimpse(sfo_feb_flights)
```
### Grading

1 point for copying and pasting the first two lines.  2 points for any command that outputs the fact that there are 68 rows in the data.

## Exercise 4
Describe the distribution of the arrival delays of these flights using a histogram and appropriate summary statistics. Hint: The summary statistics you use should depend on the shape of the distribution.

### Answer

The histogram of flights to San Fransico in February is below.
```{r 4}
ggplot(data = sfo_feb_flights, aes(x = dep_delay)) +
geom_histogram(binwidth = 10)
```
We see that this distribution is right-skewed and unimodal with a potential outlier above 200 minutes.  The descriptive statistcs are given below.
```{r}
sfo_feb_flights %>%
  summarise(median_dd = median(dep_delay), 
            IQR_dd    = IQR(dep_delay),
            n         = n())
```

### Grading
3 points for the histogram (binwidth can be different).  1 point for using words to introduce the histogram.  2 points for "unimodal."  2 points for "right-skewed."  1 point for "potential outlier."  1 point for computing the median.  1 point for computing the IQR.  1 point for complete sentences and good grammar.


## Exercise 5

### Answer

```{r}
sfo_feb_flights %>%
  group_by(origin) %>%
  summarise(median_ad = median(arr_delay), iqr_ad = IQR(arr_delay), n_flights = n())
```
JFK had more variable arrival delays than EWR.

### Grading
3 points for the code.  2 point for answering JFK.  1 point for complete sentence/grammar.

## Exercise 6
Suppose you really dislike departure delays and you want to schedule your travel in a month that minimizes your potential departure delay leaving NYC. One option is to choose the month with the lowest mean departure delay. Another option is to choose the month with the lowest median departure delay. What are the pros and cons of these two choices?

### Answer
Answers will vary.

### Grading
Give 3 points for any answer that makes sense, and partial credit for small mistakes or ambiguities.  1 point for complete sentences and grammar.

## Exercise 7
If you were selecting an airport simply based on on time departure percentage, which NYC airport would you choose to fly out of?

### Answer
I would pick LGA.

### Grading
2 points for LGA.  1 point for complete sentence with good grammar.

## Exercise 8
Consider the code below.  Tell me what the new variables `air_time_hr` and `ave_speed` describe, and what units they are measured in.
```{r 8}
nycflights <- nycflights %>%
  mutate(air_time_hr = air_time / 60,
         ave_speed = distance/air_time_hr)
```

### Answer
The variable `air_time_hr` measures the number of hours spent in the air, and it is measured in hours.  The variable `ave_speed` measures the average speed of the flight, and it is measured in miles per hour (mph).

### Grading
2 points for describing `air_time_hr` correctly.  2 points for describing `ave_speed` correctly.  1 point for full sentences with correct grammar.




